universities

### 2021-02-01 inst/universities.Rmd
consistentify universities

---
title: "universities"
output: html_document
---

```{r setup, include=FALSE}
library("hyper2")
library("magrittr")
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r cars}
a <- read.table("universities.txt",header=TRUE)
head(a,12)
```

@@

```{r, label=definehelperfunctionf}
f <- function(a,y){
  a <- subset(a,a$year==y)
  o <- function(v){  # 'v' is a character vector
    good <- v != "DNP"
    v[good] <- rank(-as.numeric(v[good]),ties.method="last")
    return(v)
  }
  out <- data.frame(o(a[,3]),o(a[,4]),o(a[,5]),o(a[,6]),o(a[,7]))
  colnames(out) <- colnames(a)[3:7]
  rownames(out) <- a[,1]
  return(out)
}
f(a,2012)
```

Now:
```{r,playerwithadvantage}
H <- hyper2(pnames=a[1:8,1])
for(i in 2013:2020){ H %<>% `+`(ordertable2supp(f(a,i)))}
H
```

Object `H` is simply the support function for the universities'
strengths for all years' observations (assumed to be independent)
2013-2020:

```{r,label=maxpcalc,cache=TRUE}
m <- maxp(H)
m
pie(m)
```

@@

H1 <- hyper2(pnames=c("AUT_pre",a[c(1:2,4:8),1]))
for(i in 2012:2016){
  b <- f(a,i)
  rownames(b)[3] <- "AUT_pre"
  H1 <- H1 + ordertable2supp(b)
} # column loop closes

H2 <- hyper2(pnames=c("AUT_post",a[c(1:2,4:8),1]))
for(i in 2017:2020){
  jj <- f(a,i)
  rownames(jj)[3] <- "AUT_post"
  H2 <- H2 + ordertable2supp(jj)
}
maxp(H2)
```

See how we reject $H_0\colon S=0$ with a p-value of about 0.00676,
significant at 1\%.

```{r}
H <- H1 + H2
maxp(H)
samep.test(H,c(1,9))
```

>>>>

---
title: "universities"
output: bookdown::html_document2
---

```{r setup, include=FALSE}
set.seed(0)
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
library("magrittr")
options("digits" = 5)
```

@@

```{r cars}
universities_table <- read.table("universities.txt",header=TRUE)
head(universities_table,12)
```

@@

```{r, label=definehelperfunctionf}
f <- function(a,y){
  a <- subset(a,a$year==y)
  o <- function(v){  # 'v' is a character vector
    good <- v != "DNP"
    v[good] <- rank(-as.numeric(v[good]),ties.method="last")
    return(v)
  }
  out <- data.frame(o(a[,3]),o(a[,4]),o(a[,5]),o(a[,6]),o(a[,7]))
  colnames(out) <- colnames(a)[3:7]
  rownames(out) <- a[,1]
  return(out)
}
f(universities_table,2012)
```

Now:
```{r,playerwithadvantage}
universities <- hyper2(pnames=universities_table[1:8,1])
for(i in 2013:2020){universities %<>% `+`(ordertable2supp(f(universities_table,i)))}
universities
```

Object `universities` is simply the support function for the
universities' strengths for all years' observations (assumed to be
independent) 2013-2020:

```{r,label=maxpcalc,cache=TRUE}
universities_maxp <- maxp(universities)
universities_maxp
pie(universities_maxp)
```

@@

H1 <- hyper2(pnames=c("AUT_pre",universities_table[c(1:2,4:8),1]))
for(i in 2012:2016){
  b <- f(universities_table,i)
  rownames(b)[3] <- "AUT_pre"
  H1 <- H1 + ordertable2supp(b)
} # column loop closes

H2 <- hyper2(pnames=c("AUT_post",universities_table[c(1:2,4:8),1]))
for(i in 2017:2020){
  jj <- f(universities_table,i)
  rownames(jj)[3] <- "AUT_post"
  H2 <- H2 + ordertable2supp(jj)
}
maxp(H2)
```

```{r}
H <- H1 + H2
maxp(H)
```

So from the above we see that the estimated post-2016 strength of AUT
is larger than the pre-2016 strength.  Is this change significant?

```{r}
samep.test(H,c("AUT_pre","AUT_post"))
```

### Package dataset {-}

Following lines create `universities.rda`, residing in the `data/`
directory of the package.

```{r,label=savecurlingdataset}
save(universities_table,universities_maxp,universities,file="universities.rda")
```
